### 2020-08-24 paper/definitions.tex
Introduction some fixes

\begin{defn}[clique]
  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected.
\end{defn}

@@

\begin{defn}[perfect graph]
  A graph $G$ is \emph{perfect} if for its every induced subgraph $G'$ we have $\chi(G') = \omega(G')$
\end{defn}

>>>>

\begin{defn}[clique]
  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected. We will denote a clique of $n$ vertices as $K_n$.
\end{defn}

@@

\begin{defn}[perfect graph]
  \label{def:perfectGraph}
  A graph $G$ is \emph{perfect} if for its every induced subgraph $G'$ we have $\chi(G') = \omega(G')$
\end{defn}

### 2020-08-24 paper/main.tex
Introduction some fixes

All graphs in this paper are finite, undirected and have no loops or parallel edges. We denote the chromatic number of graph $G$ by $\chi(G)$ and the cardinality of the largest clique of $G$ by $\omega(G)$. \emph{Coloring} of a graph means assigning every node\todo{node \rightarrow vertex everywhere (seems to be more common name)} of a graph a color. A coloring is \emph{valid} iff every two nodes sharing an edge have different colors. An \emph{optimal} coloring (if exists) is a valid coloring using only $\omega(G)$ colors.

Given a graph $G = (V,E)$, sometimes by $V(G)$ and $E(G)$ we will denote a set of nodes and edges of $G$. Given a set $X \subseteq V$ by $G[X]$ we will denote a graph induced on $X$. A graph $G$ is \emph{perfect} iff for all $X \subseteq V(G)$ we have $\chi(G[X]) = \omega(G[X])$.

\paragraph{Definitions and conventions}
	\todo{Where should we put it? Should we put all definitions here, or leave them in text?}
\begin{itemize}
	\item By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
	\item A node is $X$-complete in $G$ iff it is adjacent to all nodes in $X$.
	\item Given a path $P$, by $P^*$ we will denote its inside.
\end{itemize}

\TODO{Give some examples why perfect graphs are interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}

Given a graph $G$, its \emph{complement} $\overline{G}$ is a graph with the same vertex set and in which two distinct nodes $u, v$ are connected in $\overline{G}$ iff they are not connected in $G$. For example a clique in a graph becomes an independent set in its complement. A perfect graph theorem, first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72} states that a graph is perfect iff its complement graph is also perfect. \todo{Should we give some proof of that here? Maybe based on proof in \cite{GC03}}

>>>>

Given a graph $G$, let us consider a problem of coloring it using as few colors as possible. If $G$ contains a clique $K$ as a subgraph, we must use at least $|V(K)|$ colors to color it. This gives us a lower bound for a chromatic number $\chi(G)$ -- it is always greater or equal to the cardinality of the largest clique $\omega(G)$. The reverse is not always true, in fact we can construct a graph with no triangle and requiring arbitrarily large numbers of colors (e.g. construction by Mycielski \cite{Mycielski1955}).

Do graphs that admit coloring using only $\omega(G)$ color are "simpler" to further analyze? Not necessarily so. Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ equal to the union of $G$ and a clique $K_n$. We can see that indeed $\chi(G') = n = \omega(G')$, but it gives us no indication of the structure of $G$ or $G'$.

A definition of perfect graphs (\cref{def:perfectGraph}) states that given a graph $G$, the chromatic number and cardinality of the largest clique of \emph{its every induced subgraph} should be equal. The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum clique problem, and maximum independent set problem can be solved in polynomial time \cite{grotschel1993}

\begin{theorem}{Perfect graph theorem}
A perfect graph theorem, first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72} states that a graph is perfect iff its complement graph is also perfect. \todo{Should we give some proof of that here? Maybe based on proof in \cite{GC03}}
\end{theorem}
